Hydra Battles and Cie

### 2021-07-29 doc/hydras.tex
Use LaTeX snippets extracted with Alectryon.
- add cli to convert coq file to latex
- cut coq file with snippet
- first approch to make latex
- add paramater backend and frontend
- parse coq+rst and extract snippet to latex
- add Readme
- Make a version snippet extractor with latex conversion
- Use latex format to extract snippets
- move cutting table in move and create edit makefile
- try to make snipet in Ackerman to replace in latex file
Copy sty alectryon file and more
- copy alectryon latex assets
- Add rule to clear latex generation with make clean
- Add requirements.txt file and change

@@

>>>>

\usepackage{texments}
%%% for movies by alectryon
\usepackage{movies/snippets/assets/alectryon}
\usepackage{movies/snippets/assets/tango_subtle}

@@

\subsection{Documenting theories with alectryon}

Quotations of \coq{} source and answers are progressively replaced from copy-pasted \emph{verbatim} to automatically generated \emph{LaTeX} blocks, using Clément Pit-Claudel's \emph{Alectryon} tool~\cite{alectryonpaper, alectryongithub}.
Many thanks to Jérémy Damour and Théo Zimmermann who designed tools for maintaining consistency between the always evolving \coq{} modules and their documentation written in \emph{LaTeX}.

Besides the guarantee of consistency between theories and documentation, we hope to give a corpus for experimenting new ways of documenting the implementation of non-trivial mathematics on a proof assistant.

At present, this document is a hybrid version: Chapter~\vref{chapter:primrec} is fully adapted to \emph{Alectryon}, and we just started to re-write Chapter~\vref{chapter:hydras}.
